### 2022-11-11 dissertation/chapters/08-results.tex
✨ (results): New plots with tight bounding boxes
✨ (results): Recolored plots

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H:8}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_HgEC (Posterior)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert \theta_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0:0}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert \theta_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0:6}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert \theta_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0:7}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert \theta_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0:8}
\end{figure}

@@

      \caption{Empirical results showcasing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}

@@

      \caption{Empirical results showcasing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

\begin{sidewaysfigure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
      \caption{Descriptive plots between the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and steps.}
      \label{fig:results:standalone:descriptive:descriptive}
\end{sidewaysfigure}

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
      \caption{Critical difference plots between the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and steps.}
      \label{fig:results:standalone:descriptive:cd}
\end{figure}

@@

      \caption{Empirical results showcasing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

                                                      & \multicolumn{1}{l}{\textbf{pool}}  & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\

@@

                  air\_quality                        & 930                                & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\

@@

                  fish\_toxicity                      & 930                                & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
                  forest\_fires                       & 930                                & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\

@@

                  student\_performance                & 930                                & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
                  wine\_quality                       & 930                                & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\

@@

\begin{sidewaysfigure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all runs and steps.}
      \label{fig:results:heuristic_pool:descriptive:descriptive}
\end{sidewaysfigure}

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and steps.}
      \label{fig:results:heuristic_pool:descriptive:cd}
\end{figure}

@@

      \caption{Empirical results showcasing average rank and statistics for different population size values used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}

@@

                  air\_quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\

@@

                  fish\_toxicity                      & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
                  forest\_fires                       & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\

@@

                  student\_performance                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
                  wine\_quality                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\

@@

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
      \caption{Descriptive plots between the average ranks of \acs{BHH} with varying population sizes per dataset, across all runs and epochs.}
      \label{fig:results:population:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
      \caption{Critical Difference plots between the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
      \label{fig:results:population:descriptive:cd}
\end{figure}

@@

      \caption{Empirical results showcasing average rank and statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

                  air\_quality                        & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\

@@

                  fish\_toxicity                      & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
                  forest\_fires                       & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\

@@

                  student\_performance                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
                  wine\_quality                       & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\

@@

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all runs and epochs.}
      \label{fig:results:credit:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
      \label{fig:results:credit:descriptive:cd}
\end{figure}

@@

      \caption{Empirical results showcasing average rank and statistics for different reselection values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

                  air\_quality                        & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\

@@

                  fish\_toxicity                      & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
                  forest\_fires                       & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\

@@

                  student\_performance                & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
                  wine\_quality                       & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\

@@

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying reselection values per dataset, across all runs and epochs.}
      \label{fig:results:reselection:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying reselection values across all datasets, runs and epochs.}
      \label{fig:results:reselection:descriptive:cd}
\end{figure}

@@

      \caption{Empirical results showcasing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

                  air\_quality                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\

@@

                  fish\_toxicity                      & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
                  forest\_fires                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\

@@

                  student\_performance                & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\

>>>>

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_HgEC (Posterior)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:0}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:6}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:7}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0:8}
\end{figure}

@@

	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}

@@

	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and epochs.}
	\label{fig:results:standalone:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
	\caption{Critical difference plots for the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
	\label{fig:results:standalone:descriptive:cd}
\end{figure}

@@

	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

			                                    & \multicolumn{1}{l}{\textbf{heuristic pool}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\

@@

			air quality                         & 930                                         & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\

@@

			fish toxicity                       & 930                                         & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
			forest fires                        & 930                                         & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\

@@

			student performance                 & 930                                         & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
			wine quality                        & 930                                         & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all runs and epochs.}
	\label{fig:results:heuristic_pool:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and epochs.}
	\label{fig:results:heuristic_pool:descriptive:cd}
\end{figure}

@@

	\caption{Empirical results showing average rank and statistics for different population size values used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}

@@

			air quality                         & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\

@@

			fish toxicity                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
			forest fires                        & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\

@@

			student performance                 & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
	\caption{Descriptive plots for the average ranks of \acs{BHH} with varying population sizes per dataset, across all runs and epochs.}
	\label{fig:results:population:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
	\caption{Critical difference plots for the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
	\label{fig:results:population:descriptive:cd}
\end{figure}

@@

	\caption{Empirical results showing average rank and statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

			air quality                         & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\

@@

			fish toxicity                       & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
			forest fires                        & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\

@@

			student performance                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
			wine quality                        & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all runs and epochs.}
	\label{fig:results:credit:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
	\label{fig:results:credit:descriptive:cd}
\end{figure}

@@

	\caption{Empirical results showing average rank and statistics for different reselection values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

			air quality                         & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\

@@

			fish toxicity                       & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
			forest fires                        & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\

@@

			student performance                 & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
			wine quality                        & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection values per dataset, across all runs and epochs.}
	\label{fig:results:reselection:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reselection values across all datasets, runs and epochs.}
	\label{fig:results:reselection:descriptive:cd}
\end{figure}

@@

	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

			air quality                         & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\

@@

			fish toxicity                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
			forest fires                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\

@@

			student performance                 & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\
